A thesis draft

### 2018-12-02 res/sections/08-Background.tex
Fix typos
Fix spacing

VIBeS is a concrete example of a 5G project combining the use of SDN and NFV
technology, working in concert to provide specialized network slices for several
envisioned use-cases~\cite{vibesesa}. VIbES goals are ambitious, aiming to
demonstrate the practical convergence of satellite and 5G in a unified frame. To
reach this goal, the project specifications suggest to exploit the 5G incoming
technology and use the NFV-MANO architecture to perform first packets
elaboration and performance improvement and finally TCP/IP satellite chunk
optimization with the Performance Enhancing Proxy (PEP). The VIBES project
proposed five technical requirements:
\begin{enumerate}
  \item Analysis of the applicability of current and new Internet protocols in
  the proposed VNF-PEP architecture;
  \item Implementation of a VNF-PEP prototype;
  \item Building of a PoC test platform;
  \item VNF-PEP validation and performance tests on 5G use-cases;
  \item Demonstration test-bed management.
\end{enumerate}

@@

\subparagraph*{Network Service Header (NSH)}
The encapsulation has an header that is well defined and described in detail
in~\cite{rfc8300}. This header is composed by a 4-byte base header, and a 4-byte
Service Path Header (SPH). The base header provides information about the services
header and the kind of protocol contained as the payload, while the service path
header provides path identification and location within a define Service Path
(SP). Finally, the Context Header carries metadata.

>>>>

VIBeS is a concrete example of a 5G project combining the use of SDN and NFV
technology, working in concert to provide specialized network slices for several
envisioned use-cases~\cite{vibesesa}. VIBeS goals are ambitious, aiming to
demonstrate the practical convergence of satellite and 5G in a unified frame. To
reach this goal, the project specifications suggest to exploit the 5G incoming
technology and use the NFV-MANO architecture to perform first packets
elaboration and performance improvement and finally TCP/IP satellite chunk
optimization with the Performance Enhancing Proxy (PEP). The VIBES project
proposed five technical requirements:
\begin{enumerate}
  \item Analysis of the applicability of current and new Internet protocols in
  the proposed VNF-PEP architecture;
  \item Implementation of a VNF-PEP prototype;
  \item Building of a PoC test platform;
  \item VNF-PEP validation and performance tests on 5G use-cases;
  \item Demonstration test-bed management.
\end{enumerate}

@@

\subparagraph*{Network Service Header (NSH)}

The encapsulation has an header that is well defined and described in detail
in~\cite{rfc8300}. This header is composed by a 4-byte base header, and a 4-byte
Service Path Header (SPH). The base header provides information about the services
header and the kind of protocol contained as the payload, while the service path
header provides path identification and location within a define Service Path
(SP). Finally, the Context Header carries metadata.
